### 2022-07-22 main/chapter_2ljets.tex
add hepdata paragraph

\FloatBarrier
\section{Modelling}

So far, we have seen many histograms of background samples overlaid with
observed data.
Those backgrounds may or may not have appeared to have predicted the data well,
but no conclusions can be drawn until uncertainties are assigned to the
background and signal modelling.

@@

>>>>

\FloatBarrier
\section{Modelling}
So far, we have seen many histograms of background samples overlaid with
observed data.
Those backgrounds may or may not have appeared to have predicted the data well,
but no conclusions can be drawn until uncertainties are assigned to the
background and signal modelling.

@@

% Thanks to Jon Long, Alessia Murrone
This section only covers some of the the most peculiar or important aspects
of our signal and background modelling, and does not specify most exact
details.
Full details are publically available through the $\twoljets$
HEPData~\cite{hepdata.116034, Maguire_2017} archive our json-serialized pyhf
workspaces~\cite{cranmer2012histfactory, heinrich2021pyhf}.
\emph{Thanks to Jon~Long for collabouration in preparing this HEPData archive,
and to Alessia~Murrone for invaluable feedback on, and validation of, its
drafts.}
